Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-15 lloveras_2020.tex
Subido por ALbert

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Affilations 
%% id shold be the same with \author addressref value.
%\address[id={}]{}
\address[id=aff1]{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio (IAFE), CONICET-UBA, CC 67 - Suc 28,  (C1428ZAA) Ciudad Aut\'onoma de Buenos Aires, Argentina}

@@

%\noindent\notebyalbert{This section will summarize DEMT's main aspects and equations, only those needed to understand the paper. Nothing not needed to read this paper is provided. Also, no derivation of equations are provided. References are given so that the reader can dig deeper if so desires. Points to cover are:
%\begin{itemize}
%  \item Selected targets, instruments used. One paragraph.
%  \item Characteristics of the data (specific time series, dates, bands, etc.), SolarSoft software version used for their processing. One paragraph.
%  \item Technical aspects of DEMT (grid, regularization, off-limb data is only used) and how these differ from previous versions (rereferences). One paragraph.
%  \item What is FBE, what is LDEM, what is R. Why we care about these three quantities and what is their physical meaning should be clear. Then the final products $\Nm$ and $\Tm$, and what is their physical meaning.
%\end{itemize}
%}

@@

In the present work, data from 3 EUV bands was used. 171, 193 and 211 \AA \ in case of AIA, and 171, 195 and 284 \AA \ bands in case of EUVI. When using data from 3 EUV bands, a Gaussian model for the LDEM is able to accurately predict the tomographic emissivities \citep{frazin_2009,nuevo_2015}. In each tomographic voxel the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that allow to best reproduce the three tomographically reconstructed values of FBE in that voxel.

@@

\noindent 
{being the} average relative difference between the tomographic and the synthetic FBEs. {The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.}\\

@@

%\noindent\notebyalbert{This section will explain how the AWSoM magnetic model is used to trace the thermodynamic products of both DEMT and AWSoM along the fieldlines of AWSoM. This requires covering the following points:
%\begin{itemize}
%  \item A first paragraph qualitatively describing the process. This includes mentioning that the AWSoM products are first interpolated into the DEMT grid.
%  \item A short paragraph describing the numerical method used to trace field lines. We have a nice version of this in your previous paper.  At this point the reader should understand that for each field line we have its geometry $\mathbf{r}(s)$ as a function of the distance $s$ along the loop, with $s(1\,\mrsun)\equiv 0$. 
%  \item Explain very simply how then that for each voxel the middle point of the field line is selected and assigned the DEMT and AWSoM products of that cell. At this point the reader should understand that for each field line we have: $Q[r(s)]$, where $Q$ is any given quantity from either the DEMT model (specifically $\sqravgN$ and $\Tm$) or the AWSoM model (specifically $\Ne$ and $\Te$).
%  \item Explain fits to the DEMT results  $\sqravgN(r)$, $\Tm(r)$.
%  \item Explain then the classification of field lines.
%\end{itemize}}

@@

\begin{eqnarray}\label{Nfit}
\sqravgN &=& N_0\,\exp{\left[\,-\,\left(h/\l\right)\,/\,\left(r/\mrsun\right)\,\right]}\\
\label{Tfit}
\Tm &=& T_0\,+\,m\,h
\end{eqnarray}
\noindent
where $h \equiv r - 1\,\mrsun$ is the coronal height measured from the photosphere. In the electron density fit, $\l\,[\mrsun]$ is the density scale height and $N_0\,[\cminvc]$ is the electron density at the footpoint ($h=0$) of the loop. In the electron temperature fit, $m\,[\MK/\mrsun]$ is the slope and $T_0\,[\MK]$ is the electron temperature at the footpoint of the loop. The slope $m$ is the radial gradient of the electron temperature along the loop, which we denote as $m = \dr\Tm$ hereafter, being $\dr\equiv\er\cdot\nabla$ the radial derivative operator, where $\er$ is the heliocentric radial unit vector.

@@

{Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies. As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop. Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}. In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and {considering time-averaged heating rates.}}
\noindent
\notebyalbert{Modifiqué la descripción del test estadístico en el próximo párrafo . Estuve leyendo un poco y hay que asegurarse que esto quede escrito bien. Yo busqué la frase más vaga que me parece tiene un sentido científico claro. Aquí hay una versión de divulgación:\\
{\tt www.statisticshowto.datasciencecentral.com/confidence-level/}\\
pero tener cuidado con esto: busquen ``Statistical Significance" en la Wikipedia, y lea la breve sección ``Redefining significance" al final del artículo.}

@@

{
\begin{itemize}
\item Type 0: closed-small-down with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
\item Type I: closed-small-up with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
\item Type II: closed-large-up with footpoints in the range $|{\rm latitude}|>40\mdeg$. 
\item Type III: open with footpoint in the range $|{\rm latitude}|>60\mdeg$.
\end{itemize}
}
{Legs of type down turn out to have a significant population only for closed-small loops. In the case of closed-large loops and open field lines, there are very few cases of type down. Hence, the requirement of being up for legs of type II and III is included above to select the vastly dominating population in each case}. \\
In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed. {As shown in Section \ref{demt_res}, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}

@@

%\noindent\notebyalbert{This section will summarize how loop integrated energy quantities are computed from the DEMT products and the AWSoM magetic model alone. The summary will not include any derivation and will refer to Cecilia's paper. Only the results that are relevant are to be explicited. Start by explaining the model and assumptions, and end up summarizing the loop-integrated products (radiative and conductive fluxes). At the end the reader should understand that their sum is the enery input flux required at the coronal base to maintain the loop stable. This should be a very short section, as it is a summary of a single previous paper.}

@@

%\noindent\notebyalbert{This section will show first the DEMT products in the form of Carrington maps at three heights, for the two target rotations. It will then show the latitude/longitude location of the four types of  magnetic loops (defined in Section 2.3) at a sample height. Then, for the each type of loop, we will show histograms of the values of different DEMT products traced along them, charerizing in a quantitative fashion the DEMT results in distinct magnetic structures. It will also include a quantitative comparison between the two target rotations of the median values of the DEMT products in each type of loop.}

@@

{As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations. Three different heights {of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of tomographic \diego{grid} ($1.025\,\mrsun$), {the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}. Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}). Thick-black {curves indicate} the {open/closed boundaries of the magnetic field of the} AWSoM model.

@@

Figure \ref{gradt_demt} shows frequency histograms \diego{$\dr\Tm$} for legs of type 0, I, II and III. The lack of population around values close to zero is due to the requirement $|\rhoTr| > 0.5$ which discards quasi-isothermal legs. For both rotations, {the median value of the temperature radial gradient is ${\rm Md}\left(\dr\Tm\right) \approx -2.5$, $+2.3$ and $+2.4\,\MK/\mrsun$} for legs of type 0, I and II, respectively.

@@

{{Adding the} radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}. Note that for type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$. As shown by \citet{maccormack_2017}, {this affects only the smallest sized loops of the type 0}, and it is {most probably} due to the limited temperature sensitivity of the instrumental passbands. The radiative loss term is {here calculated based on plasma emission detected by three coronal bands of EUVI or AIA. Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range. As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, {being characterized by $\phi_c<0$. \vfill}} % NOTA el vfill

@@

%\noindent\notebyalbert{This section will show the results of AWSoM for $N_e$ and $T_e$, and how they compare with the corresponding results of DEMT ($\sqravgN$ and $\Tm$). It will first show the Carrington maps of $N_e$ and $T_e$ at the same three heights we showed the same maps for the DEMT results.  As the two targets are highly axis-symmetric, a first quantitative comparison between AWSoM and DEMT will be shown as longitude-averaged latitudinal profiles of the results of both models at a sample height. Then we will show the lat/lon location of loops of type I, II and III at a middle height, just loke for DEMT results. To make comparisons in distinct magnetic structures, we will show the average radial dependence of results for loops of type I, II and III, overplotting the AWSoM and the DEMT results. For the tree types of loops we will show histograms of the DEMT and AWSoM products along field lines. This is a LOT of information from which and we need to pull out a few clear conclusions.}

@@

%\notebyalbert{Propongo que Diego escriba una primer sección limpia, ordenada. Lo que vos mandarías al Solar Physics, sin asteriscos ni nada raro. Expresate con párrafos limpios. Si querés destacar algo para discutir ponelo como una nota en rojo al final del párrafo correspondiente, no en el medio de los mismos. Yo creo que esto debe estructurarse así: 
%\begin{enumerate}
%\item Un párrafo (breve) de que se hizo, esto contextualiza. 
%\item Dos o tres párrafos sobre los resultados 3.1. Esto es: resultados per se de cada rotación y como comparan (mencionando el tema incertezas). Estructura 3D del streamer en CAPAS, revelada observacionalmente en forma global por DEMT, esto incluye UP/DOWN loops. Explicar que con AIA no andamos bien en CHs. O sí? Energía.
%\item Uno o dos párrafos sobre los resultados 3.2. Como compara AWSoM con DEMT. En forma breve. Vale la pena explicar que DOWN loops no se puede.
%\item Luego un párrafo sobre next steps. Esto puede incluir nuevas cosas con AIA-4, el Eclipse, otras rotaciones de mayor intensidad.
%\end{enumerate}
%}

@@

\noindent
\notebyalbert{Diego, agregá las sección de agradecimientos, fijándote como lo hicimos para tu paper anterior. Vos seguro debes agradecer a la beca, Ceci tambien (fijate en su paper), y todos los de aqui deberemos agraecer grants. Armalo como puedas y luego lo revisamos.}

%% Figure 
%
% \begin{figure} 
% \centerline{\includegraphics[width=0.5\textwidth,clip=]{<fig.eps>}}
% \caption{}%\label{fig:?}
% \end{figure}

%% Table
%
% \begin{table}
% \caption{}%\label{tbl:?}
% \begin{tabular}{}     
% \hline
% \multicolumn{2}{c}{<>}
% <data>
% \hline
% \end{tabular}
% \end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Appendix
%
% \appendix

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Acknowledgements
%
 \begin{acks}
D.G.Ll. and C.M.C. acknowledges CONICET doctoral fellowship (Res. Nr. 4870) to IAFE that supported his participation in this research.
The authors acknowledge \diego{ANPCyT grant 2012/0973 and CONICET grant PIP \# 11220120100403 estos son viejos?} to IAFE that partially supported their participation in this research
 \end{acks}

%%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Bibliography
%
% Using BibTeX
%
\bibliographystyle{spr-mp-sola}
\bibliography{solphys_dglloveras}  
%
% Without BibTeX 
% \begin{thebibliography}{}
% \bibitem[\protect\citeauthoryear{Author}{Year}]{key}
%   <bibliographical entry>
%
% \bibitem[\protect\citeauthoryear{}{}]{}
%   
%  
% \end{thebibliography}

>>>>

\address[id=aff1]{Instituto de Astronom\'{\i}a y F\'{\i}sica del Espacio (IAFE), CONICET-UBA, CC 67 - Suc 28,  (C1428ZAA) Ciudad Aut\'onoma de Buenos Aires, Argentina}

@@

@@

\albert{In this work,} data from thre EUV bands was \albert{used:} 171, 193 and 211 \AA \ in \albert{the} case of AIA, and 171, 195 and 284 \AA \ bands in \albert{the} case of EUVI. When using data from \albert{three bands}, a Gaussian model for the LDEM is able to accurately predict the tomographic emissivities \citep{frazin_2009,nuevo_2015}. In each tomographic voxel the problem is then reduced to finding the values of the three free parameters of the Gaussian (centroid, standard deviation, and area) that allow to best reproduce the three tomographically reconstructed values of FBE in that voxel.

@@

\noindent 
{being the} average relative difference between the tomographic and the synthetic FBEs. {The final product of DEMT is in the form of 3D maps of the LDEM-averaged quantities $\sqravgN$ and $\Tm$, as well as of the measure $R$.}

@@

@@

\begin{eqnarray}\label{Nfit}
\sqravgN &=& N_0\,\exp{\left[\,-\,\left(h/\l\right)\,/\,\left(r/\mrsun\right)\,\right]}\\
\label{Tfit}
\Tm &=& T_0\,+\,m\,h
\end{eqnarray}

\noindent
where $h \equiv r - 1\,\mrsun$ is the coronal height measured from the photosphere. In the electron density fit, $\l\,[\mrsun]$ is the density scale height and $N_0\,[\cminvc]$ is the electron density at the footpoint ($h=0$) of the loop. In the electron temperature fit, $m\,[\MK/\mrsun]$ is the slope and $T_0\,[\MK]$ is the electron temperature at the footpoint of the loop. The slope $m$ is the radial gradient of the electron temperature along the loop, which we denote as $m = \dr\Tm$ hereafter, being $\dr\equiv\er\cdot\nabla$ the radial derivative operator, where $\er$ is the heliocentric radial unit vector.

@@

{Coronal magnetic structures for which temperature increases/decreases with height (in the inner corona) were dubbed as “up”/“down” loops by \citet{huang_2012} and \citet{nuevo_2013}, who first reported their presence by means of DEMT studies. As speculated by the authors of those works, loops of type down can be expected if the heating deposition is strongly confined near the coronal base of a magnetic loop. Down loops were first predicted by \citet{serio_1981}, and later on by \citet{aschwanden_2002}. In a recent study, \citet{schiff_2016} reproduced both down and up loops by means of numerical simulations, using a 1D steady-state model and {considering time-averaged heating rates.}}

@@

\begin{itemize}
\item Type 0: closed-small-down with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
\item Type I: closed-small-up with footpoints in the range $|{\rm latitude}|<50\mdeg$. 
\item Type II: closed-large-up with footpoints in the range $|{\rm latitude}|>40\mdeg$. 
\item Type III: open with footpoint in the range $|{\rm latitude}|>60\mdeg$.
\end{itemize}

{Legs of type down turn out to have a significant population only for closed-small loops. In the case of closed-large loops and open field lines, there are very few cases of type down. Hence, the requirement of being up for legs of type II and III is included above to select the vastly dominating population in each case}. \\
In Section \ref{resu}, the results of both the DEMT and AWSoM models in the distinct magnetic strucures are statistically analysed. {As shown in Section \ref{demt_res}, classification of legs from type 0 through II allows studying the streamer belt in three distinct, progressively outer layers.}

@@

@@

@@

{As an example,} Figures \ref{carmaps_demt_2082} and \ref{carmaps_demt_2208} show {latitude-longitude} maps of DEMT results for both {rotations. Three different heights {of interest are selected from the tomographic grid}, providing also a detailed 3D view of the tomographic results: the lowest height of \albert{the} tomographic grid ($1.025\,\mrsun$), {the lowest height where the AWSoM results are fully} consistent with coronal conditions ($1.065\,\mrsun$), and a middle height of the tomographic grid ($1.105\mrsun$)}. Black voxels correspond to non-reconstructed voxels ({see} Section \ref{demt}). Thick-black {curves indicate} the {open/closed boundaries of the magnetic field of the} AWSoM model.

@@

Figure \ref{gradt_demt} shows frequency histograms \albert{of $\dr\Tm$} for legs of type 0, I, II and III. The lack of population around values close to zero is due to the requirement $|\rhoTr| > 0.5$ which discards quasi-isothermal legs. For both rotations, {the median value of the temperature radial gradient is ${\rm Md}\left(\dr\Tm\right) \approx -2.5$, $+2.3$ and $+2.4\,\MK/\mrsun$} for legs of type 0, I and II, respectively.

@@

{{Adding the} radiative and conductive terms, the characteristic energy input flux at the coronal base is in the range $\phi_h\approx 0.5-1.5 \times 10^5\,\erg\,\cminvs\,\s^{-1}$, depending on the rotation and the type of {loop, matching the values reported by} \citet{maccormack_2017}. Note that for type 0 loops there is a marginal population characterized by the unphysical result $\phi_h<0$. As shown by \citet{maccormack_2017}, {this affects only the smallest sized loops of the type 0}, and it is {most probably} due to the limited temperature sensitivity of the instrumental passbands. The radiative loss term is {here calculated based on plasma emission detected by three coronal bands of EUVI or AIA. Though accounting for most of the coronal plasma, there surely is additional emission out of the instrumental sensitivity range. As a result,} the positive term $\phi_r$ is most likely underestimated, leading to values $\phi_h<0$ in loops of type 0, {being characterized by $\phi_c<0$.}}

@@

@@

@@

\begin{acks}
D.G.Ll. and C.M.C. \albert{acknowledge} CONICET doctoral \albert{fellowships} (Res. Nr. 4870) to IAFE that supported \albert{their} participation in this research. \albert{D.G.Ll, A.M.V., F.A.N. and C.M.C. acknowledge ANPCyT grant 2016/0221 to IAFE that partially supported their participation in this research. A.M.V. also acknowledges UBACyT grant XXXX to FCEyN-UBA and IAFE that partially supported his participation in this research.}
\end{acks}

\bibliographystyle{spr-mp-sola}
\bibliography{solphys_dglloveras}
